---
title: "proj_arima"
author: "lbq"
date: "2020/11/28"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 
```{r}
getwd()
library(forecast)
TSLA.full = read.csv("11_31scale.csv", header = T)
```
for simple multilinear regression model 

$Y_i = \beta X_i+ \varepsilon_i$

```{r}
TSLA.full$Date = as.Date(TSLA.full$Date, format = "%Y-%m-%d")
TSLA.full.lm = lm(Close ~ Volume + OilPrice + deaths + DPRIME + TOTALSA, data = TSLA.full)
summary(TSLA.full.lm)
plot(TSLA.full.lm, which = 1)
```

```{r}
library(leaps)
regsubsets.out = regsubsets(
  Close ~ Volume + OilPrice + deaths + DPRIME + TOTALSA, data = TSLA.full,
  nbest = 1,
  nvmax = NULL,
  method = "exhaustive"
)
plot(regsubsets.out , scale = "r2", main = "R^2")
plot(regsubsets.out , scale = "adjr2", main = "Adjust R^2")
plot(regsubsets.out , scale = "Cp", main = " Mallow's Cp ")
plot(regsubsets.out , main = "BIC")
```
There is no evidence that the deaths is significant

```{r}
TSLA.no.deaths.lm = lm(Close ~ Volume + OilPrice + DPRIME + TOTALSA, data = TSLA.full)
summary(TSLA.no.deaths.lm)
plot(TSLA.no.deaths.lm, which = 1)
acf(TSLA.no.deaths.lm$residuals)
```
From acf plot the errors are highly correlated.
```{r}
plot(TSLA.full$Date, TSLA.full$Close, type = 'l',
     xlab = "Date", ylab = "Close", main = "Price with date")
```
the time series is not stationary so we log the Price and diff it
```{r}
Price = log(TSLA.full$Close)
ndiffs(Price)
Close.diff = diff(TSLA.full$Close, 1)
ndiffs(Close.diff)
Close.diff = diff(Close.diff, 1)
plot(TSLA.full$Date[1:length(Close.diff)] ,Close.diff, type = 'l',
     xlab = "Date", ylab = "log Close", main = "log Price with date")
acf(Close.diff)
pacf(Close.diff)

```



```{r}
auto.arima(TSLA.full$Close, trace = T, xreg = cbind(TSLA.full$Volume, TSLA.full$OilPrice, TSLA.full$DPRIME, TSLA.full$TOTALSA))

```

The best model is ARIMA(5, 1, 5)
SO 
```{r}
ARIMA.m = arima(TSLA.full$Close, 
                order = c(5, 1, 5),
                xreg = cbind(TSLA.full$Volume, TSLA.full$OilPrice, TSLA.full$DPRIME, TSLA.full$TOTALSA),
                method="ML")
summary(ARIMA.m)

```
```{r}
plot(ARIMA.m$residuals)
acf(ARIMA.m$residuals)
```

model is 
\[
x_t = 0.5073 x_{t-1} -0.4876 x_{t-2} + 0.3036 x_{t-3}-0.3949x_{t-4} -0.4415 x_{t-5} + \varepsilon_t -0.6016\varepsilon_{t-1}
 - 0.6246 \varepsilon_{t-2}  -0.2823 \varepsilon_{t-3} + 0.4034 \varepsilon_{t-4} + 0.3198\varepsilon_{t-5} + 0.0018*oilprice + 0.1007*dPRIME + -34.8192*TOTALSA
\]
























```{r}
price = ts(data = TSLA.full$Close)
plot(price)
acf(price)
ndiffs(price)
price.diff2 = diff(price, 2)
ndiffs(price.diff2)
price.diff21 = diff(price.diff2, 1)
ndiffs(price.diff21)
acf(price.diff21)
pacf(price.diff21)
plot(price.diff21)

auto.arima(price, trace = T)

arima.model = arima(price, order = c(3,2,0), method = "ML")

summary(arima.model)

plot(arima.model$residuals)

acf(arima.model$residuals)

qqnorm(arima.model$residuals)
Box.test(arima.model$residuals, type = "Ljung-Box")
pred = predict(arima.model, 10)
pred
plot(c(2615:2625),price[(length(price)-10) : length(price)-1], type = 'l')
lines(pred$pred, col = "red")

```























